---
title: "Motivaciones Virgen de la Puerta-factoMineR"
author: "Rodolfo León"
format: html
date: last-modified
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
suppressPackageStartupMessages(library(tidyverse))
library(FactoMineR)
library(factoextra)
library(corrplot)
library(psych)
```

## Principal Components Analysis - PCA

```{r}
#Load the data
otuzco <- read_csv2("data/Motivaciones_Virgen_de_Otuzco_short_UTF8.csv")
summary(otuzco)
```

```{r}
res <- PCA(otuzco[, 2:23])   # This is a list
summary(res)
```

```{r}
#Run the PCA with supplementary variables
res <- PCA(otuzco, quanti.sup = 24:37)
summary(res, rbelements = Inf)
```

```{r}
# Description of the dimensions
dimdesc(res)
dimdesc(res, proba = 0.2)
```

```{r}
plot(res, cex = 0.8, invisible = "quali", title = "Individual PCA Graph")
# plot(res, cex = 0.8, habillage = "Competition")
```

```{r}
# Confidence ellipses around the categories
plotellipses(res)
```

```{r}
# Graphs for dimensions 1 and 2
plot(res, choix = "ind", cex = 0.8, habillage = 13, title = "Individual PCA Graph", axes = 1:2)
plot(res, choix = "var", title = "variables PCA Graph", axes = 1:2)
```

```{r}
# Graphs for dimensions 3 and 4
plot(res, choix = "ind", cex = 0.8, habillage = 13, title = "Individual PCA Graph", axes = 3:4)
plot(res, choix = "var", title = "variables PCA Graph", axes = 3:4)
```

```{r}
# Selecting individuals
plot(res, choix = "ind", cex = 0.8, habillage = 5, select = "cos2 0.7")
plot(res, choix = "ind", cex = 0.8, habillage = 5, select = "contrib 15")
```

```{r}
# Select variables
plot(res, choix ="var", select = "contrib = 15")
```

```{r}
plot(res, cex = 0.8, habillage = 13, select = "cos2 0.7", title = "Motivaciones Otuzco", cex.main = 1.1, cex.axis = 0.9, shadow = TRUE, auto = "y")
```

### Explore the results

#### 1.Top Eigenvalues

```{r}
res$eig[2:23,]
```

```{r}
fviz_eig(res, addlabels = TRUE, ncp = 15) + theme_grey()
```

#### 2. Top individuals

##### Coordinates of individuals on the principal components

```{r}
res$ind$coord[2:37,]
```

#### 3. Top 15 Variables

```{r}
res$var$coord[2:23, ]
```

```{r}
fviz_pca_ind(res, select.ind = list(contrib = 15), axes=c(1,2), repel = T) + theme_grey()
```

##### Cos2 : quality of representation of individuals on the principal components

```{r}
res$ind$cos2[1:15,]
```

##### Contribution of individuals to the principal components

```{r}
res$ind$contrib[1:15,]
```

### Scree plot (Contributions graph)

```{r}
fviz_eig(res, ncp = 15, addlabels = TRUE)
```

### Visualize individuals and variables on the first two principal components

```{r}
fviz_pca_ind(res, select.ind = list(contrib = 15), col.ind = "cos2", col.var = "contrib", repel = TRUE)
```

### Correlation circle

```{r}

fviz_pca_var(res, select.var = list(contrib = 15), col.var = "cos2", repel = TRUE)
```
